An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2023-11-21 article.tex
attempt at fixing my xgboost definitions.

% FIXME: Make it clearer why you did this "Because the purpose of the analysis was to identify relationships between variables and since there was no single outcome variable of interest an XGBoosted tree was created for each variable using the other variables as predictors
% FIXME: forward reference here "XGBoosted trees, described in more detail below...
% FIXME: I found this a bit confusing as a 'new reader'. How about describing this process as a set of analyses:
% Step 1: Separate analyses of operating cost and revenue: XGBoosted models were constructed for each of these variables, with the variable as the response and all other variables (with the exception of operating cost and revenue) as predictors.
% Step 2: For each of the operating cost and revenue models, an analysis of the inter-relationships between the ten most important predictors based on the XGBoosted model.
% Set 3: Analysis of profit (difference between...): etc
% Then say that the results of the analyses in Set 3 were not considered further due to how crap they were.
As the purpose of the analysis was to identify relationships between variables and to show how they interact, an XGBoosted tree was created for every variable. Each tree included all variables except the economic variables (operating cost and revenue from grape sales), which were only included within their own trees as response variables. Separately profit (the difference between revenue and operational costs) was looked at in prior analyses (see appendix) but the results were not included due to low average loss values and model stability. This meant that every variable would have a measure of its importance to other variables (see Section \ref{sec:importance}), which was used to show the highly interrelated nature of variables within vineyards. The interaction between variables was illustrated using Sankey and Chord diagrams; with variable importance measures being used to show the strength of connection between the respective predictor variable and the response (see section \ref{sec:importance}).

@@

% FIXME: We need a digestable description of XGBoost for readers of this article.

>>>>

XGBoosted models were constructed with operational cost and grape revenue as the predicted variables. The analyses were aimed at uncovering what factors influenced these variables and to what extent. As the purpose of the analysis was to identify relationships between variables and to show how they interact, an XGBoosted tree was created for each of the predictor variables as well. Trees for the predictor variables did not include operational cost or grape revenue as predictors. By creating an XGBoosted tree for each variable it meant that every variable would have a measure of its relative importance to every other variable (see Section \ref{sec:importance}). Together these models were used to measure the interrelationships of the ten most important variables in determining operational cost and grape revenue using variable importance. These measures of relative importance were used to illustrate the highly interrelated nature of variables within vineyards. The interaction between variables was depicted through the use of Sankey and Chord diagrams; with variable importance measures being used to show the strength of connection between the respective predictor variable and the response (see section \ref{sec:importance}).

@@

Due to constraints from the XGBoost library region could only be incorporated as a one-hot-encoded variable when used as a predictor. To better show what variables were related to region overall, another XGBoost tree was created with Region as the predicted value. The difference for this model was that relative variable importance would only be measured for each region specifically, as opposed to a variables overall importance in determining region. Separately profit (the difference between revenue and operational costs) and year was looked at in prior analyses (see appendix) but these results were not included due to low average loss values and model stability. 
XGBoosted trees are an ensemble method that combines multiple decision trees together to create a more accurate predictive model. The gradient boosting aspect of the ensemble is the use of a loss function used to create new decision trees that add to the ensemble. Each new tree created is done so using a loss function that is optimised iteratively to improve upon prior tree's predictive power. The loss function can be any convex function, allowing gradient descent to traverse the loss space until, no improvements can be made via traversal. Because the loss function is only required to be convex, both classifiers and regressors can be used. Regularisation methods can also be incorporated to help prevent over fitting.
